manual-geostat-TMB

### 2019-01-22 manual-geostat-TMB.Rmd
Fix residuals (they need to be calculated on the original data... of course)

#### Save preditions from model
```{r}
  predictions <- stats::predict(m, newdata = grid_locs)$data
# predictions$resids <- residuals(m) # randomized quantile residuals but not working
  glimpse(predictions) # est = predicted values

@@

#### Check residuals
```{r}
#ggplot(predictions, aes(X, Y, col = resids)) + scale_colour_gradient2() +
#  geom_point() + facet_wrap(~year)

#hist(predictions$resids)
#qqnorm(predictions$resids);abline(a = 0, b = 1)
```

>>>>

#### Save preditions from model
```{r}
predictions <- predict(m, newdata = grid_locs)$data
glimpse(predictions) # est = predicted values

# Make predictions on original data:
predictions_original <- predict(m)$data
predictions_original$resids <- residuals(m) # randomized quantile residuals
glimpse(predictions_original) # est = predicted values

@@

#### Check residuals
```{r}
ggplot(predictions_original, aes(X, Y, col = resids)) + scale_colour_gradient2() +
 geom_point() + facet_wrap(~year)

hist(predictions_original$resids)
qqnorm(predictions_original$resids);abline(a = 0, b = 1)
```
